### 2022-03-30 conclusion/conclusion.tex
more

This extension of Ehoh to \ehohii{} finished the third cycle. Inspired by our
approach of extending techniques designed for weaker logics to work in the
context of richer logics, we decided to look for ways in which superposition can
assimilate the most successful techniques of SAT solving. Extension of hidden
literals was straightforward, but finding the right way to tame their infinite
nature in the first-order case, as well as the right way to integrate equality
in their definition was challenging. Predicate elimination posed challenges in
terms of finding the exact conditions in which it can be integrated with the
saturation loop. We first observed that blocked clause elimination destroys the
completeness of superposition calculus when we noticed that Zipperposition does
not prove some problems when it is enabled. After sifting through tens of
benchmarks and carefully examining the debugging information we realized that
this was not due to a bug in the implementation but due to incompatibility of
blocked clause elimination with redundancy criterion. In the end, we were left
somewhat disappointed to learn that SAT techniques do not scale well to be used
as superposition simplification techniques. However, we learned that they are
very successful as preprocessing techniques.

>>>>

This extension of Ehoh to \ehohii{} finished the third cycle. Inspired by our
approach of extending techniques designed for weaker logics to work in the
context of richer logics, we decided to look for ways in which superposition can
assimilate the most successful techniques of SAT solving. Extension of hidden
literals was straightforward, but finding the right way to tame their infinite
nature in the first-order case, as well as the right way to integrate equality
in their definition was challenging. Predicate elimination posed challenges in
terms of finding the exact conditions in which it can be integrated with the
saturation loop. We first observed that blocked clause elimination destroys the
completeness of superposition calculus when we noticed that Zipperposition does
not prove some problems when the technique is enabled. After sifting through tens of
benchmarks and carefully examining the debugging information we realized that
this was not due to a bug in the implementation but due to incompatibility of
blocked clause elimination with redundancy criterion. In the end, we were left
somewhat disappointed to learn that SAT techniques do not scale good enough to be used
as superposition simplification techniques. However, we learned that they are
very successful as preprocessing techniques.

### 2022-03-30 ehoh2/ehoh2.tex
summary_eng
more

  \looseness=-1
  On the trajectory to \ehohii{}, we developed, together with colleagues, three
  superposition calculi:\ \lfsup{} for $\lambda$-free higher-order logic
  \cite{bbcw-21-lfho}, \lsup{} for a higher-order logic with
  $\lambda$-abstra\-ction but no Booleans \cite{bbtvw-21-sup-lam}, and \osup{}
  for full higher-order logic \cite{bbtvw-21-sup-lam}. These milestones allowed
  us to carefully estimate how the increased reasoning capabilities of each
  calculus influence its performance. We also developed a complete and efficient
  unification algorithm (Chapter \ref{ch:unif}) which can easily be customized
  to trade bits of its completeness for efficiency. Practically oriented work,
  described in Chapters \ref{ch:bools} and \ref{ch:ho-techniques},
  helped us gauge how much reasoning power we lose by using more intuitive and
  more easily controllable incomplete rules. Both the theoretical and the
  practical lines of our work met in this chapter, resulting in a prover that
  outperforms the competition on the benchmarks from proof assistants.

>>>>

  \looseness=-1
  On the trajectory to \ehohii{}, we developed, together with colleagues, three
  superposition calculi:\ \lfsup{} for $\lambda$-free higher-order logic
  \cite{bbcw-21-lfho}, \lsup{} for a higher-order logic with
  $\lambda$-abstra\-ction but no Booleans \cite{bbtvw-21-sup-lam}, and \osup{}
  for full higher-order logic \cite{bbtv-21-full-ho-sup}. These milestones allowed
  us to carefully estimate how the increased reasoning capabilities of each
  calculus influence its performance. We also developed a complete and efficient
  unification algorithm (Chapter \ref{ch:unif}) which can easily be customized
  to trade bits of its completeness for efficiency. Practically oriented work,
  described in Chapters \ref{ch:bools} and \ref{ch:ho-techniques},
  helped us gauge how much reasoning power we lose by using more intuitive and
  more easily controllable incomplete rules. Both the theoretical and the
  practical lines of our work met in this chapter, resulting in a prover that
  outperforms the competition on the benchmarks from proof assistants.
